---
title: "Sedation with Benzodiazepines in MICU"
subtitle: "Analysis for Alcalde"
author: "Elizabeth Franco, Jen Cortes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(pander)
library(FSA)
library(dplyr)
if (!exists("data.demograph")) data.demograph <- readRDS("Analysis/data_demograph.Rds")
if (!exists("data.assessments")) data.assessments <- readRDS("Analysis/data_assessments.Rds")
if (!exists("data.lfts")) data.lfts <- readRDS("Analysis/data_lfts.Rds")
if (!exists("data.sedatives")) data.sedatives <- readRDS("Analysis/data_sedatives.Rds")
```

### Continuous Data

Shapiro-Wilk normality test is performed and if the data is not normally distributed (the p-value is < 0.05), then the Mann-Whitney test is used to compare the medians of the my.groups.

If the data is normally distributed, an F-test is performed to determine if the my.groups have equal variances (p-value is $\ge$ 0.05) and then the appropriate t-test (with or without equal variances) is used to compare the means of the my.groups.

```{r echo=FALSE, warning=FALSE}
temp <- data.demograph %>%
    mutate(group = ifelse(bzd == TRUE, "BZD", "No BZD"))
my.group <- temp$group
temp <- select(temp, -group, -bzd)

cont <- sapply(temp, is.numeric)
test <- temp[,c(cont)]

ds1 <- lapply(test, tapply, my.group, Summarize)
ds2 <- lapply(ds1, do.call, what=cbind)

## a p < 0.05 implies the data is not normally distributed
sw1 <- lapply(test, shapiro.test)

## if not normally distributed, use non-parametric test
## if var.test$p.value >= 0.05 then variances are equal
tt3 <- lapply(test, function(x) 
    if(shapiro.test(x) >= 0.05) {
        wilcox.test(x ~ my.group)
    } else if(var.test(x ~ my.group)$p.value >= 0.05) {
        t.test(x ~ my.group)
    } else {
        t.test(x ~ my.group, var.equal=TRUE)
    })

np1 <- lapply(test, function(x) wilcox.test(x ~ my.group))

ds3 <- lapply(seq_along(ds1), function(i) list(results = ds2[[i]], normality = sw1[[i]], comparison = tt3[[i]]))

names(ds3) <- names(ds1)

pander(ds3)
```

### Categorical Data

Data is evaluated using the Chi-squared test. 

```{r echo=FALSE, warning=FALSE}
test <- temp[,!c(cont)]
test <- select(test, -pie.id, -diagnosis) 

ds1 <- lapply(test, function(x) table(x, my.group))
ds2 <- lapply(test, function(x) Summarize(my.group ~ x, percent="column", addtotal=FALSE))
# csq <- lapply(ds1, summary)

csq <- lapply(test, function(x) 
    if(is.factor(x)) {
        chisq.test(x, my.group)
    } else if(is.logical(x) & sum(x, na.rm=TRUE) > 0) {
        chisq.test(x, my.group)
    } else {
        "Chi-squared could not be performed"
    })

ds3 <- lapply(seq_along(ds1), function(i) list(counts = ds1[[i]], percents = ds2[[i]], chi.sq = csq[[i]]))
names(ds3) <- names(ds1)

pander(ds3)
```


### References

Data was processed using `r R.Version()$version.string` on a `r R.Version()$platform` system.

Prepared by: Brian Gulbis

```{r echo=FALSE}
citation()
```
