---
title: "Sedation with Benzodiazepines in MICU"
subtitle: "Analysis for Alcalde"
author: "Elizabeth Franco, Jen Cortes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(BGTools)
library(pander)
library(FSA)
library(dplyr)
if (!exists("data.demograph")) data.demograph <- readRDS("Analysis/data_demograph.Rds")
if (!exists("data.assessments")) data.assessments <- readRDS("Analysis/data_assessments.Rds")
if (!exists("data.lfts")) data.lfts <- readRDS("Analysis/data_lfts.Rds")
if (!exists("data.sedatives")) data.sedatives <- readRDS("Analysis/data_sedatives.Rds")
```

#### Continuous Data

Shapiro-Wilk normality test is performed and if the data is not normally distributed (the p-value is < 0.05), then the Mann-Whitney test is used to compare the medians of the groups.

If the data is normally distributed, an F-test is performed to determine if the groups have equal variances (p-value is $\ge$ 0.05) and then the appropriate t-test (with or without equal variances) is used to compare the means of the my.groups.

#### Categorical Data

Data is evaluated using the Chi-squared test. 

## Results

```{r echo=FALSE, warning=FALSE}
temp <- data.demograph %>%
    mutate(group = ifelse(bzd == TRUE, "BZD", "No BZD"))
my.group <- temp$group
temp <- select(temp, -group, -bzd)

results <- analyze_data(temp, my.group)
pander(results)
```


```{r}
library(purrr)
library(broom)

temp <- data.demograph %>%
    mutate(group = ifelse(bzd == TRUE, "BZD", "No BZD")) %>%
    group_by(group) %>%
    select(-bzd, -pie.id)



cont <- map_lgl(temp, is.numeric)

test <- keep(temp, is.numeric) %>% 
    bind_cols(select(temp, group)) %>% 
    # group_by(group) %>%
    # do(tidy(summary(.)))
    
    slice_rows("group") %>% 
    by_slice(map, summary)

test2 <- temp %>% split(.$group) %>% map(summary)

pander(test$.out)
```

## References

Data was processed using `r R.Version()$version.string` on a `r R.Version()$platform` system.

Prepared by: Brian Gulbis

```{r echo=FALSE}
citation()
```
