---
title: "Sedation with Benzodiazepines in MICU"
author: "Elizabeth Franco, Jen Cortes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
subtitle: Analysis for Alcalde
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(BGTools)
library(pander)
library(FSA)
library(dplyr)
library(purrr)
if (!exists("data.demograph")) data.demograph <- readRDS("Analysis/data_demograph.Rds")
if (!exists("data.assessments")) data.assessments <- readRDS("Analysis/data_assessments.Rds")
if (!exists("data.lfts")) data.lfts <- readRDS("Analysis/data_lfts.Rds")
if (!exists("data.sedatives")) data.sedatives <- readRDS("Analysis/data_sedatives.Rds")
```

#### Continuous Data

Shapiro-Wilk normality test is performed and if the data is not normally distributed (the p-value is < 0.05), then the Mann-Whitney test is used to compare the medians of the groups.

If the data is normally distributed, an F-test is performed to determine if the groups have equal variances (p-value is $\ge$ 0.05) and then the appropriate t-test (with or without equal variances) is used to compare the means of the my.groups.

#### Categorical Data

Data is evaluated using the Chi-squared test. 

## Results

```{r echo=FALSE, warning=FALSE}
test <- data.demograph %>%
    mutate(group = ifelse(bzd == TRUE, "BZD", "No BZD")) %>%
    select(-pie.id, -bzd, -diagnosis)

results <- analyze_data(test)
pander(results)
```

## Sedatives

```{r echo=FALSE, warning=FALSE}
sed <- data.sedatives %>% 
    mutate(group = ifelse(bzd == TRUE, "BZD", "No BZD")) %>%
    select(med, group, time.wt.avg.rate:total.dose) %>%
    slice_rows("med") %>%
    by_slice(analyze_data)

names(sed$.out) <- sed$med
pander(sed$.out)
```

## References

Data was processed using `r R.Version()$version.string` on a `r R.Version()$platform` system.

Prepared by: Brian Gulbis

```{r echo=FALSE}
citation()
```
